HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-06-30 paper/main.tex
Corrected Charles uni and acknowledgements

\newcommand*{\affaddr}[1]{#1} 
\newcommand*{\affmark}[1][*]{\textsuperscript{#1}}
\newcommand*{\email}[1]{\texttt{#1}}

@@

\author{
Alexandra Birch\textsuperscript{1}, Barry Haddow\textsuperscript{1}, Ond{\v{r}}ej Bojar\textsuperscript{2}, Omri Abend\textsuperscript{3}\\
\textsuperscript{1}School of Informatics, University of Edinburgh\\
\textsuperscript{2}Institute of Formal and Applied Linguistics, Charles University in Prague\\
\textsuperscript{3}School of Computer Science and Engineering, Hebrew University of Jerusalem\\
\texttt{a.birch@ed.ac.uk, bhaddow@inf.ed.ac.uk}\\
\texttt{bojar@ufal.mff.cuni.cz, oabend@cs.huji.ac.il}\\
}

@@

%\section*{Acknowledgments}

>>>>

\newcommand{\GrantNo}{644402}
\newcommand{\ProjectName}{HimL}
\newcommand{\ProjectType}{Horizon 2020 Innovation Action}

@@

\author{
Alexandra Birch\textsuperscript{1}, Barry Haddow\textsuperscript{1}, Ond{\v{r}}ej Bojar\textsuperscript{2}, Omri Abend\textsuperscript{3}\\
\textsuperscript{1}School of Informatics, University of Edinburgh\\
\textsuperscript{2} Charles University in Prague, Faculty of Mathematics and Physics\\
\textsuperscript{3}School of Computer Science and Engineering, Hebrew University of Jerusalem\\
\texttt{a.birch@ed.ac.uk, bhaddow@inf.ed.ac.uk}\\
\texttt{bojar@ufal.mff.cuni.cz, oabend@cs.huji.ac.il}\\
}

@@

\section*{Acknowledgments}
{T}his work was conducted within the scope of the \ProjectType, which has received funding from the European Union’s Horizon 2020 research and innovation programme under grant agreement No \GrantNo (\ProjectName).
